---
title: "CV_master"
author: "Pascale"
date: "3/13/2020"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## master data for Chips

# load data

```{r, echo=FALSE}
c.dat<-read.csv("CyrilforCV.csv")
head(c.dat)
colnames(c.dat)[c(10)] <- "relRkm"
# add julian day of last detection date
c.dat$last_detect<-format(as.POSIXct(strptime(c.dat$last_arrival,format="%Y-%m-%d %H:%M:%S", tz="")),"%j")
c.dat$Date<-as.Date(c.dat$last_arrival,"%Y-%m-%d")

j.dat<-read.csv("JSATS_CV_v3.csv")
head(j.dat)
colnames(j.dat)[c(7,9)] <- c("wateryear","Run")
# add julian day of last detection date
j.dat$last_detect<-format(as.POSIXct(strptime(j.dat$last_arrival,format="%m/%d/%Y %H:%M", tz="")),"%j")
j.dat$Date<-as.Date(j.dat$last_arrival,"%m/%d/%Y %H:%M")

yb.dat<-read.csv("YB1213CV.csv")
head(yb.dat)
colnames(yb.dat)[c(9)] <- "wateryear"
# add julian day of last detection date
yb.dat$last_detect<-format(as.POSIXct(strptime(yb.dat$last_arrival,format="%m/%d/%Y %H:%M", tz="")),"%j")
yb.dat$Date<-as.Date(yb.dat$last_arrival,"%m/%d/%Y %H:%M")

ybus.dat<-read.csv("ybusCV_v2.csv")
head(ybus.dat)
# add julian day of last detection date
ybus.dat$last_detect<-format(as.POSIXct(strptime(ybus.dat$last_arrival,format="%Y-%m-%d %H:%M:%S", tz="")),"%j")
ybus.dat$Date<-as.Date(ybus.dat$last_arrival,"%Y-%m-%d")
```

# combine

```{r}
chip.dat<-rbind(c.dat[,c(-1,-4)], j.dat[,c(-3,-10)], yb.dat[,c(-4)], ybus.dat[,c(-1)])
head(chip.dat)
```

# simplify release groups

```{r}
unique(chip.dat$Release_Group)
grps<-data.frame(
  Release_Group = c("Battle Creek", "Middle Sacramento River", "Upper Sacramento River",
            "American River", "Tidal Delta", "Feather River", "Mill Creek", "Butte Creek"),
  Release_Group_SAIL = c("Upper Sacramento River","Middle Sacramento River","Upper Sacramento River",
            "Middle Sacramento River","Tidal Delta", "Middle Sacramento River",
            "Middle Sacramento River","Middle Sacramento River"), stringsAsFactors = FALSE)

chip.dat<-merge(chip.dat, grps, by="Release_Group")
chip.dat$last_detect<-as.numeric(chip.dat$last_detect)
```

## master data for benicia

# load data

```{r, echo=FALSE}
c.ben<-read.csv("CyrilforCV_ben.csv")
head(c.ben)
colnames(c.ben)[c(10)] <- "relRkm"
c.ben$last_detect<-format(as.POSIXct(strptime(c.ben$last_arrival,format="%Y-%m-%d %H:%M:%S", tz="")),"%j")
c.ben$Date<-as.Date(c.ben$last_arrival,"%Y-%m-%d")

j.ben<-read.csv("JSATS_CV_ben.csv")
head(j.ben)
colnames(j.ben)[c(8,10)] <- c("wateryear","Run")
j.ben$last_detect<-format(as.POSIXct(strptime(j.ben$last_arrival,format="%Y-%m-%d %H:%M:%S", tz="")),"%j")
j.ben$Date<-as.Date(j.ben$last_arrival,"%Y-%m-%d")
```

# combine

```{r}
ben.dat<-rbind(c.ben[,c(-1)], j.ben[,c(-1,-11)])
head(ben.dat)
```

# simplify release groups

```{r}
unique(ben.dat$Release_Group)

ben.dat<-merge(ben.dat, grps, by="Release_Group")

ben.dat$last_detect<-as.numeric(ben.dat$last_detect)
```

## use "salmon-season" instead of Julian Day

```{r}
dates<-read.csv("STB_CHN_Dates_updated.csv")
dates$Date<-as.Date(dates$Date)
head(dates)

chip.dat<-merge(chip.dat, dates, by="Date", all.x=TRUE)
ben.dat<-merge(ben.dat, dates, by="Date", all.x=TRUE)

write.csv(chip.dat, "masterCV_chip.csv")
write.csv(ben.dat, "masterCV_benicia.csv")
```

## heatmaps 

```{r, echo=FALSE}
library(tidyverse)
```

# chips

# summarize CV in travel time
```{r}
CV_chip.tt <- chip.dat %>%
  filter(FishID !="Delta2013-043")%>%
  group_by(wateryear, Route, Release_Group_SAIL, add=TRUE) %>%
  summarize(count = n(),
            mean = mean(travel_time, na.rm=TRUE),
            SD = sd(travel_time, na.rm=TRUE))%>%
  mutate(CV=SD/mean)
```

# plot CV in travel time
```{r, fig.width=14, fig.height=12}
ggplot(CV_chip.tt, aes(wateryear, Route)) +
  geom_raster(aes(fill = CV)) +
  scale_fill_distiller(palette = "Blues", direction = -1)+ 
  theme(
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_line(colour = "grey50"),
    panel.ontop = TRUE
  )+
  facet_wrap(~ Release_Group_SAIL)
```

# summarize CV in date of last detection
```{r}
CV_chip.ld <- chip.dat %>%
  filter(FishID !="Delta2013-043")%>%
  group_by(wateryear, Route, Release_Group_SAIL, add=TRUE) %>%
  summarize(count = n(),
            mean = mean(Salmon.Season, na.rm=TRUE),
            SD = sd(Salmon.Season, na.rm=TRUE))%>%
  mutate(CV=SD/mean)
```

# plot CV in date of last detection
```{r, fig.width=14, fig.height=12}
ggplot(CV_chip.ld, aes(wateryear, Route)) +
  geom_raster(aes(fill = CV)) +
  scale_fill_distiller(palette = "Blues", direction = -1)+ #previously used "Spectral"
  theme(
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_line(colour = "grey50"),
    panel.ontop = TRUE
  )+
  facet_wrap(~ Release_Group_SAIL)
```

# benicia

# summarize CV in travel time
```{r}
CV_ben.tt <- ben.dat %>%
  group_by(wateryear, Route, Release_Group_SAIL, add=TRUE) %>%
  summarize(count = n(),
            mean = mean(travel_time, na.rm=TRUE),
            SD = sd(travel_time, na.rm=TRUE))%>%
  mutate(CV=SD/mean)
```

# plot CV in travel time
```{r, fig.width=14, fig.height=12}
ggplot(CV_ben.tt, aes(wateryear, Route)) +
  geom_raster(aes(fill = CV)) +
  scale_fill_distiller(palette = "Blues", direction = -1)+ 
  theme(
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_line(colour = "grey50"),
    panel.ontop = TRUE
  )+
  facet_wrap(~ Release_Group_SAIL)
```

# summarize CV in last detection
```{r}
CV_ben.ld <- ben.dat %>%
  group_by(wateryear, Route, Release_Group_SAIL, add=TRUE) %>%
  summarize(count = n(),
            mean = mean(Salmon.Season, na.rm=TRUE),
            SD = sd(Salmon.Season, na.rm=TRUE))%>%
  mutate(CV=SD/mean)
```

# plot CV in last detection
```{r, fig.width=14, fig.height=12}
ggplot(CV_ben.ld, aes(wateryear, Route)) +
  geom_raster(aes(fill = CV)) +
  scale_fill_distiller(palette = "Blues", direction = -1)+ 
  theme(
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_line(colour = "grey50"),
    panel.ontop = TRUE
  )+
  facet_wrap(~ Release_Group_SAIL)
```

